---
title: "ignore"
output: html_document
---

#final product - index.rmd - md_document output
# _config.yml theme: "" title: ""

#TO DO LIST
#convert all fit files to csv (https://maxcandocia.com/article/2017/Sep/22/converting-garmin-fit-to-csv/)
#take date off of meet column
#create function matching activities to athlete 
#match kudos id to activity id


```{r setup, include=FALSE}
library(rvest)
library(stringr)
library(tidyverse)
```
Justin  !
Jackson !
Owen    !
Mike Finn !
Plumb   !
Elliot - Just have activities file ! 
Alec - Just have activities file   !
Bill - !
Turtle 
Calvin
Chris Brenk
Byver 
Ruben 
Ben
Cian
Meatsauce
Freshmen 

https://maxcandocia.com/article/2017/Sep/22/converting-garmin-fit-to-csv/
```{r}

scraper <- function(x){
url <- x
web <- read_html(url)
data <- html_nodes(web, ".xc .panel-heading-normal-text , .xc .panel-heading-text")
data_strp <- str_replace_all(html_text(data), '\n','') 
data_strp <- str_replace_all(data_strp, '\t','')
data_strp <- str_replace_all(data_strp, "\\.",'')
data_strp <- str_replace_all(data_strp, ':', '\\.')

# 1 = meet + date, 2 = distance, 3 = time, 4 = place 
meet_name <- 0:4
distance <- 0:4
time <- 0:4
place <- 0:4
date <- 0:4
k <- 1
for(i in seq(1, 42, by=4)){
  meet_name[k] = data_strp[i]
  distance[k] = data_strp[i+1]
  time[k] = data_strp[i+2]
  place[k] = data_strp[i+3]
k <- k + 1  
}
val <- data.frame(meet_name, distance, time, place)
return(val)
}
justin <- scraper("https://www.tfrrs.org/athletes/5492056/St_Olaf/Justin_Furcich.html")
owen <- scraper("https://www.tfrrs.org/athletes/5990269/St_Olaf/Owen_Wright.html")
jack <- scraper("https://www.tfrrs.org/athletes/5990267/St_Olaf/Jackson_Simon.html")
finn <- scraper("https://www.tfrrs.org/athletes/6430274/St_Olaf/Michael_Finn.html")
elliot <- scraper("https://www.tfrrs.org/athletes/5990262/St_Olaf/Elliot_Kadrofske.html")
plumb <- scraper("https://xc.tfrrs.org/athletes/5492067.html")
birdo <- scraper("https://www.tfrrs.org/athletes/5492064/St_Olaf/Alec_Kirtley.html")

#https://www.tfrrs.org/athletes/5492056/St_Olaf/Justin_Furcich.html
#https://www.tfrrs.org/athletes/5990269/St_Olaf/Owen_Wright.html
#https://www.tfrrs.org/athletes/5990267/St_Olaf/Jackson_Simon.html
#https://www.tfrrs.org/athletes/6430274/St_Olaf/Michael_Finn.html
#Plumb
#https://xc.tfrrs.org/athletes/5492067.html
#https://www.tfrrs.org/athletes/5990262/St_Olaf/Elliot_Kadrofske.html
#https://www.tfrrs.org/athletes/5492064/St_Olaf/Alec_Kirtley.html

sca <- list(justin, owen, jack, finn, elliot, plumb, birdo)
write.csv(sca,"test.csv")
test <- read.csv("test.csv")
test
```

